---
title: "Homework2.3"
author: "Yuanyuan Lin"
date: "2019/9/19"
output: pdf_document
---

```{r setup, include=FALSE}
library(knitr)                ## loading the entire knitr package
library(ggplot2)              ## the only tidyverse library you need is ggplot2
library(esquisse)             ## use esquisse to setup the basic plots

library(kableExtra)
library(magrittr)
opts_chunk$set(echo = TRUE)
```

# Class assignment:

Using the MPG dataset, which is available with the ggplot2 library, produce a document that includes the following elements: headers, text, tables, and plots.  

Tables should include a comparison of city and highway mileage by the class of car and the best three car models for city and highway mileage for all the years in which data is available.  

Plot the data displaying as much of the data as you can. Put continuous variables on the axes and include a locally smoothed regression line to show the relationship with mileage.  Also make a box plot comparing city and highway MPG by class of car.  


## Tables

Comparison of city and highway mileage by the class of car 
```{r include = FALSE}
knitr::opts_chunk$set(echo=FALSE)

data(mpg)     ## load the data

mpg$cyl <- as.factor(mpg$cyl)   ## convert discrete variables to factors so that they plot
mpg$drv <- as.factor(mpg$drv)   ## as different colors, not gradations of one color

mpg$cty <- as.double(mpg$cty)
                                
class <- unique(mpg$class)      ## define a vector for car classes

cty_mean <- rep(0, length(class))  ## define variables to hold mean mileage
hwy_mean <- rep(0,length(class))   ## for each class of car

for(i in 1:length(class)){                          ## calculate the mean city and 
  cty_mean[i] = mean(mpg$cty[mpg$class==class[i]])  ## highway mileage for each 
  hwy_mean[i] = mean(mpg$hwy[mpg$class==class[i]])  ## class of car
}

cty_mean <- round(cty_mean, 2)                      ## round the results to 2 decimal pla
hwy_mean <- round(hwy_mean, 2)

tbl_1 <- cbind(class, cty_mean,hwy_mean)      ## form an array for the table



kable(tbl_1, format = "latex", booktabs=TRUE, digits = 2,     ## call kable to make the table
      col.names = c("Class", "City", "Highway"), 
      caption = "Mean City and Highway MPG by Car Class" )      

tbl_1




```

Best three car models for city and highway mileage for all the years
```{r}
tbl_1 <- cbind(class, cty_mean,hwy_mean)      ## form an array for the table



kable(tbl_1, format = "latex", booktabs=TRUE, digits = 2,     ## call kable to make the table
      col.names = c("Class", "City", "Highway"), 
      caption = "Mean City and Highway MPG by Car Class" )      

tbl_1
```